Longitudinal Data Analysis with the ABCD Study

### 2024-03-18 index.qmd
updating landing page

---
#title: "Longitudinal Analysis"

format:
  html:
    css: styles.css
    #theme: cosmo
    page-layout: custom
    grid:
      sidebar-width: 200px
      body-width: 2000px
      margin-width: 0px
      gutter-width: 0rem
---

Test

>>>>

---
#title: "Longitudinal Data Analysis with the ABCD Study"
format:
  html:
    css: styles.css

---

# Welcome to the Longitudinal Data Analysis Project

This ongoing project, guided by the Biostatistics Working Group of the [Adolescent Brain Cognitive Development (ABCD) Study](https://abcdstudy.org/), aims to democratize access to longitudinal data analysis through practical examples and tutorials.

::: {.callout-important}
**Note**: This project is currently in beta. [Examples](https://opendevsci.github.io/LongDev-ABCD/examples/examples.html) are under development and may not be ready for direct application. Your feedback and contributions are invaluable to us—join us in enhancing these resources. For more details on contributing, visit our [GitHub repository](https://github.com/OpenDevSci/LongDev-ABCD) and our [Contribution Guide](https://github.com/OpenDevSci/LongDev-ABCD/blob/main/docs/Contributing.md).
:::

## Our Mission

We aim to provide accessible resources for those interested in longitudinal data analysis, using publicly available data from the ABCD Study to showcase various methodologies and techniques.

## Why This Project?

- **Publicly Available Code**: Future updates will include ready-to-use code examples for your research and educational needs. See some initial examples [here](https://opendevsci.github.io/LongDev-ABCD/examples/examples.html) or in the `examples` folder of our [GitHub repository](https://github.com/OpenDevSci/LongDev-ABCD)
- **Open Source Collaboration**: Engage with our community to contribute, learn, and share insights on longitudinal data analysis.
- **Educational Resource**: Gain comprehensive knowledge in using GitHub, R, RMarkdown/Quarto, and various longitudinal analysis methods with our guidance.

## How to Contribute

- **Provide New Examples**: Enhance our repository with your unique analysis examples.
- **Help With Documentation**: Contribute to making our documentation more comprehensive and user-friendly.
- **Repository Maintenance**: Assist in the ongoing maintenance and accessibility of our GitHub repository.

For more information on how you can make an impact, check out our [Contribution Guide](https://github.com/OpenDevSci/LongDev-ABCD/blob/main/docs/Contributing.md).

## Project Resources

- **[Code Examples](https://github.com/OpenDevSci/LongDev-ABCD)**: Discover a variety of analysis examples to guide your research.
- **[Documentation](https://github.com/orgs/OpenDevSci/projects/13)**: Get detailed insights into our project's progress, tasks, and timelines.
- **[Community Discussion Forum](https://github.com/orgs/OpenDevSci/discussions)**: Connect with fellow researchers and enthusiasts in our dedicated forum.

## About Us

We are a team driven by the mission to make longitudinal data analysis more accessible and understandable. Our collective effort focuses on fostering an open source community where knowledge and skills in research methodologies can flourish.

**Together, let's advance the field of data analysis.**
